---
title: "Penguins Love RMarkdown"
author: "Carina"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  bookdown::html_document2:
    toc: true
    toc_float: true
---

The YAML header in the .Rmd file specifies how your document will be outputted. I like to use `html` so that I can have a floating table of contents, and if you want to be able to caption figures and reference them in the text and/or if you want numbered sections then use `bookdown::html_document2`. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

There's an invisible setup chunk here where I specify global options for all chunks going forward. If I'm making analysis reports to share I'll usually set `echo = FALSE` so that my code isn't cluttering up the document, and for chunks where neither the code nor the output needs to be shown I'll set `include = FALSE` in those individual chunk options.

For this doc though, I'll leave `echo = TRUE` so you can see both the code and the output. 

# Set up 

Load packages first. I've named the below chunk `packages` (even though you can't see that name in the output html file) to make it easier to refer to when I'm editing the .Rmd file.

```{r}
# install.packages("palmerpenguins")
library(palmerpenguins)
library(magrittr)
library(tidyverse)
```

The `magrittr` package is super handy for the `%<>%` pipe. Notice how I can put text in backticks to make them look like code in the output document.

Let's take a look at the first 6 rows (or the "head") of our penguins dataset:

```{r}
head(penguins)
```

We can also look at the structure of the dataset to get some info about the variables:

```{r}
str(penguins)
```

# Do male and female penguins have different bill lengths?

We can do a *t*-test to answer this question.

```{r}
results = t.test(bill_length_mm ~ sex, data = penguins) %>% 
  print()
```

I've saved the results as the variable `results` so that I can use them when writing up a results section:

There is a statistically significant difference between male and female penguins' bill lengths, *t*(`r results$parameter %>% round(2)`) = `r results$statistic %>% round(2)`, *p* < .001.

To add in-line R code (as opposed to code in chunks), place the code in backticks and put `r` at the start of your code.

## Plot the results

```{r plot, fig.cap = "Difference in bill length between male and female penguins"}
penguins %>% 
  drop_na() %>% 
  ggplot(aes(x = sex, y = bill_length_mm, colour = sex, fill = sex)) +
  geom_violin(alpha = .4) +
  geom_jitter(alpha = .6) +
  scale_colour_manual(values = c("slateblue1", "tan1")) +
  scale_fill_manual(values = c("slateblue1", "tan1")) +
  guides(colour = FALSE, fill = FALSE) +
  stat_summary(fun = mean, geom = "point", colour = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = .1, colour = "black") +
  theme_bw() +
  labs(x = "Sex", y = "Bill length (mm)") +
  scale_x_discrete(labels = c("female" = "Female", "male" = "Male"))
```

Figure \@ref(fig:plot) indicates that female penguins have shorter bills than do males. 

To be able to refer to the figure, the code chunk containing the figure code needs to have both a name and a caption. 

